---
title: "Intro_ResProStr"
# output: rmarkdown::html_vignette
output: pdf_document
vignette: >
  %\VignetteIndexEntry{Intro_RPS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### About package

The goal of ResProStr package is to provide the functionality for the Research Program Strategy (ResProStr) as explained in the article **"Hypothesis-testing demands trustworthy data-a simulation approach to inferential statistics advocating the research program strategy"** by *Krefeld-Schwalb, Witte & Zenker (2018)*. For more details about the theory, please have a look at the main paper and related technical appendix document: 

- **Main paper:** https://www.frontiersin.org/articles/10.3389/fpsyg.2018.00460/full

- **Appendix:** https://osf.io/gaetn/

### About ResProStr Description

Every step of our simulation mimics 100 t-values for one-sided t-tests sampled from two normal distributions featuring the same variance but different means. One mean is set to zero (x0), the other mean corresponds to the effect size $\delta$ of the focal condition (x1), such that $\displaystyle x1\sim Normal(\delta,1)$ and 
$\displaystyle x0\sim Normal(0,1)$ The following equation is used o define the sample size, $N_{min}$, drawn from these distributions that is needed to achieve the power $(1-\beta)$ given $\alpha$-error, and the effect size $\delta$.

\begin{equation} N = (z(1-\alpha)+z(1-\beta))^2/(\delta/\sqrt(2))^2 \end{equation}
We next calculated the t-value based on the difference of the means, $\mu$, of these distributions. 

\begin{equation} \displaystyle t = (\mu_{x1}-\mu_{x0})/\sqrt{2/n}\end{equation}

The consecutive steps of the Research Program Strategy (ResProStr) is summarized below; 

1. Preliminary Discovery:$p \leq \alpha, \alpha \leq .05$,  unknown $\beta$

2. Substantial Discovery: $p \leq \alpha,\alpha \leq .05$,  known $\beta$

3. Preliminary Falsification: $\displaystyle\frac{L(d>0|x)}{L(d=0|x)} > \frac{1-\beta}{\alpha}$ 

4. Substantial Falsification: $\displaystyle\frac{L(d>\delta|x)}{L(d=0|x)} > \frac{1-\beta}{\alpha}$

5. Preliminary Verification: $\displaystyle\frac{L(d =\delta|x)}{L(d=0|x)} > \frac{1-\beta}{\alpha}$

6. Substanstial Verification:$\displaystyle\frac{L(d =\delta|x)}{L(d=0|x)} > \frac{1-\beta}{\alpha} \cap \frac{L(d|x)}{L(d=\delta|x)} > \frac{pdf(P50|d)}{pdf(P95|d)} > 4$

In order to calculate these proportions we use the **density of the respective t-distributions** and calculated the one-sided *p*-values, *p*, as well as the likelihood, L. The Wald-criterion, $\frac{1-\beta}{\alpha}$, is applied for interpreting the corresponding likelihood ratios in steps 3 to 5. As a criterion for substantial verification in step 6 we further use the ratio of the probability density function, pdf, at the $50$'th and $95$'th percentiles, $P50$ and $P95$, respectively.

### Simulation Example 

```{r echo = T, eval = T}
## Number of simulated tests
Nsample = 100

## Level of significance
alpha = 0.05

### Different effect sizes
effectSize = 0.2

### Different Power
pow = 0.95
```

Here, in the simulation example, the goal is to estimate the minimum sample size $N_{min}$ by using the effect size, $\delta$, and test power, $(1-\beta)$, which together determine the induction quality of data, between the conditions, $d=$ [`r effectSize`] and $(1-\beta)=$ [`r pow`]. 

For the above parameters, the estimated sample size is obtained as;

```{r echo=T, eval = T}
samph1 <- ResProStr::samplesH1(Nsample = 100, alpha=alpha, effectSize = effectSize, pow = pow)
round(samph1$Nest, 0)
```

### Visualization

For the visualizations of the output, separate functions are given in **ModelVis.R** file and the wrap-up function (**plot_RPS.R**) is ready to use by selection of the figures when all the necessary inputs are provided. Distinctly, the **ggplot2 syntax** was used for all figures in the package so the obtained graphs are different from the ones you observed in the Shinny app!

The main tool is **plot_RPS.R**, as a wrap-up function to make a general visualization of the outputs by making selection. To illustrate,

```{r}
sampH0 <- ResProStr::samplesH0(Nsample = 100, alpha = 0.05, 
                               effectSize = 0.1, pow = 0.95)

sampH1 <- ResProStr::samplesH1(Nsample = 100, alpha = 0.05, 
                                effectSize = 0.1, pow = 0.95)

sampEmp <- ResProStr::samplesEmp(Nsample = 100, N = 30, Temp = 3, 
                                 alphaEmp = 0.05)

# About plotting, you can consider different selections by select argumen
ResProStr::plot_RPS(sampH0 = sampH0, sampH1 = sampH1, sampEmp = sampleEmp, select = 1)
```

One can use the **Figure functions** separately,

```{r}
sampH1 <- ResProStr::samplesH1(Nsample = 100, alpha = 0.05, 
                               effectSize = 0.2, pow = 0.95)

# Run this function manually if you want from ModelVis.R script
# Make sure that all necessary packages are already installed and ready to use 
# lapply(c("ggplot2", "ggpubr", "ggtext"), require, character.only = TRUE)
# figure1(sampH1)
```

### Summarizing Results

For the tabularization of the outputs, separate functions are given in 
**TableOutputs.R** file and the wrap-up function (**table_RPS.R**) is ready to use by selection of the different tables when all the necessary inputs are provided. Similar to visualization, ready to publish tables are generated by using **gt package**. 

```{r}
# The below results are necessary before creating tables generally
# By using sampleH1
samp30 <- ResProStr::samples30(Nsample = 100, alpha = 0.05, effectSize = 0.2,
          pow = 0.95, samp = sampH1)

sampEmp0 <- ResProStr::samplesEmp0(Nsample = 100, N = 30, Temp = 3, 
                                   alphaEmp = 0.05)

# The creation of the 
# Table 1: Proportion of correct positive results (prior to data collection)

ResProStr::table_RPS(sampH0 = sampH0, sampH1 = sampH1, sampEmp = sampEmp,
          sampEmp0 = sampEmp0, samp30 = samp30, select = 1)
```


















